\documentclass[10pt]{scrbook}
\usepackage[utf8]{inputenc}
\usepackage{array}
\usepackage[a4paper,left=0.3in,right=0.3in,top=0.15in,bottom=0.15in]{geometry}
\usepackage{amssymb}
\usepackage{tabularx}
\usepackage{setspace}
\usepackage{footmisc}
\usepackage{ragged2e} %for aligning
\pagenumbering{gobble}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage[none]{hyphenat}
\usepackage{gensymb}
\usepackage{xcolor}
\usepackage{boldline}
\usepackage{xcolor}
\hypersetup{
    colorlinks,
    linkcolor={red!50!black},
    citecolor={blue!50!black},
    urlcolor={blue!80!black}
}
\setkomafont{section}{\mysection}
\newcommand{\mysection}[1]{%
    \sf\bf%
    \setlength{\fboxsep}{0cm}%already boxed
    \colorbox{lightgray}{%
        \begin{minipage}{\linewidth}%
            \vspace*{2pt}%Space before
            #1
            \vspace*{2pt}%Space after
        \end{minipage}%
    }}
\begin{document}
\begin{flushleft}
\Huge{\textbf{SIDDHARTH GANERIWALA}}
\end{flushleft}
\normalsize
Junior Under-Graduate \hspace{7.5cm} \hfill{siddharth.ganeriwala1996@gmail.com}
\newline
Department of Chemical Engineering \hfill{sidgane@iitk.ac.in} 
\newline Indian Institute of Technology, Kanpur \hfill{+91 749 923 3350}
\section*{Educational Qualifications}

\begin{center}
\begin{tabular}{| >{\centering}m{2cm} | >{\centering}m{4.5cm} | >{\centering}m{5.5cm} | c |}
\hline
\textbf{Year} & \textbf{Degree} & \textbf{Institute} & \textbf{CPI / \%} \\ 
\hline
2019 (expected)	& Bachelor of Technology, Chemical Engineering & Indian Institute of Technology, Kanpur	& 7.8\textsuperscript{$\ast$} \\
\hline
2015 & CBSE ( XII Board ) & Sunbeam Lahartara , Varanasi & 95.4 \% \\
\hline
2013 & ICSE ( X Board)	& St.John's D.L.W. , Varanasi & 89.9 \% \\
\hline
\end{tabular}
\end{center}
\begin{flushright}
    \small{$\ast$ After 4th Semester}
    $\quad$
\end{flushright}

\section*{Academic Achievements}
\begin{itemize}
\item Secured an \textbf{All India Rank 5330} in JEE Advanced 2015 conducted by IIT Bombay and about 200,000 students appeared for the exam.
\item Secured an \textbf{All India Rank 2050} in JEE Main 2015 conducted by CBSE and 1,500,000 students took the exam.
\item Secured State Rank 10 and \textbf{National Rank 62} in SOF - National Cyber Olympiad. 
\item Secured State Rank 22 in SOF - International Mathematic Olympiad. 
\end{itemize}

\section*{Work Experience}
\begin{itemize}
\item \textbf{NewYork Office,IIT Kanpur} \hfill\textit{May'17-July'17}\\
\textit{Android App Developer under Prof. Manindra Agarawal , IITK}
\begin{itemize}
\item Integrated Fabric library in app which made it easier to monitor the crash reports and real time analytics of the app.
\item Improved UI/UX of the app by implementing features associated with menus, viewpagers, card views, preference layouts etc. adhering to Google’s Material Design guidelines.
\item Served as the peer mentor to all other inters and the Team-Lead for a team of 3 interns.

\end{itemize}
\end{itemize}

\section*{Projects}
\begin{itemize}
\item \textbf{HTTP Proxy Server } \hfill\textit{August'17 - November'17}
\begin{itemize}
\item Course Project for CS425A ( Computer Networks) done under Prof. Dheeraj Sanghi .
\item Server handled HTTP GET, HEAD and POST requests and rejected all other types of requests.
\item Enforced nthentication using username and password and supported User-Based request filtering using domain. 
\item Implemented caching and load balancing to reduce bandwidth usage and load on web servers %and optimally ditribute load on different proxy servers.
\end{itemize}

\item \textbf{Entrance Identification} \hfill\textit{January'16 - April'16}
\begin{itemize}
\item Project done under Programming Club as a semester long project. 
\item Developed a Python program which used an RFID scanned input to check the validity of an ID card
\item Python code was uploaded on Raspberry PI. 
\end{itemize}

\item \textbf{Inter IIT Android App}\hfill\textit{August'16 - December'16}
\begin{itemize}
\item Developed the Front-end for the official Inter IIT Sports meet Android App.
\item Incorporated features such as Gallery, LiveHelp, Result and Event's Schedule in the app. 
\end{itemize}

\item \textbf{Techkriti App} \hfill\textit{January'17 - April'17}
\begin{itemize}
\item Worked on the previous year's Techkriti App to incorporate new features like LiveHelp, etc.
\item Improvised the User Interface of the app and notification system. 
\end{itemize}

\item \textbf{Stamping Machine} \hfill\textit{July'16-November'16}
\begin{itemize}
\item Course Project for TA202 ( Manufacturing Processes-II ) done under Prof. Niraj Sinha.
\item Designed and fabricated a model to stamp on a roll of paper at a fixed interval.
\item Validated the computer aided design of its prototype with virtual testing in Solidworks.
\end{itemize}
\newpage 

\item \textbf{Vertical Lift Bridge} \hfill\textit{January'17-April'17}
\begin{itemize}
\item Course Project for TA201 ( Manufacturing Processes) done under Prof. Shashank Shekhar.
\item Fabricated a model of Vertical Lift Bridge whose height could be varied to give the way to large ships.
\item Prepared the computer aided design of its prototype on Solidworks.
\item Awarded as \textbf{Best Sectional Project} among many other projects. 
\end{itemize}

\item \textbf{Herbal Soap} \hfill\textit{January'17-April'17}
\begin{itemize}
\item Course Project for CHE261 ( Chemical Process Industries) done under Prof. Animangsu Ghatak.
\item Prepared a soap using all herbal products like Neem,Rose etc and various pure oils like Coconaut Oil, Olive Oil etc.
\end{itemize}
\end{itemize}


\section*{Relevant Coursework}

\begin{center}
\begin{tabular}{m{5cm}  m{5cm} m{5cm}}

 
 Introduction to C Programming &
  Data Structure And Algorithm &
  Introduction To Electronics\\

 Calculus and Analytic Geometry &
 Linear Algebra and ODE &
 Chemical Process Industries \\
  Fluid Mechanics &
  Numerical Methods &
  Chemical Thermodynamics \\
  Mass Transfer \textsuperscript{$\dagger$}&
  Heat Transfer \textsuperscript{$\dagger$}&
  Chem. Process Simulation lab\textsuperscript{$\dagger$}\\


\end{tabular}

\begin{flushright}
    
    \small{$\dagger$ - Ongoing}
\end{flushright}
\end{center}


\section*{Technical Skills}
\begin{itemize}
\item \textbf{Programming Skills: } C/C++, Python, Java, Bash. 
\item \textbf{Software and Utilities: } Git, \LaTeX, Arduino, SolidWorks, Android Studio, Processing, Linux/Shell, Matlab.
\item \textbf{Skills: } Android Development
\item \textbf{Operating System: } Windows, Ubuntu  
\end{itemize}

\section*{Position of Responsibility}
\begin{itemize}
\item \textbf{Secretary, Electronics Club, IIT Kanpur} \hfill\textit{May'16 - April'17}
\begin{itemize}
\item Organized events and institute level electronic workshops to introduce the freshmen  to basic electronics. 
\item Mentored a short-semester long project of the club
\item Managed budget and the day to day functioning of the club.
\end{itemize}
\item \textbf{Company Coordinator, Students' Placement Office, IIT Kanpur}\hfill\textit{July'16 - April'17}
\begin{itemize}
\item Attended HRs and managed their hospitality during PPTs and placement.
\item Helped with the smooth conduction of the placement interviews during December'16.
\item Coordinated the students and the Training and Placement Department to avoid misguidance.
\item Directed the students about the procedures of interviews, group discussions, dress code, etc.
\end{itemize}
\item \textbf{Coordinator, TOSC, Techkriti'17}\hfill\textit{July'16 - April'17}
\begin{itemize}
\item Convinced various institues of Varanasi to participate in the school level competition TOSC.
\item Conducted the first-round in Varanasi which witnessed the participation of 700 students.
\end{itemize}

\end{itemize}

\section*{Extra-Curricular Activities}
\begin{itemize}
\item Secured 2\textsuperscript{nd} position in Embedded and 4\textsuperscript{th} position in ElectroWiz inter hall technical event,Takneek'16.
\item Fabricated block stacking robot and designed its electronic circuit in inter hall technical event,Takneek'15.
\item Implemented Simon Says Game using basic electronic IC's as a part of Winter Camp by Electronics Club.
\item Designed Snake Game GUI and its controls using processing as a part of Winter Camp by Electronics Club.  
\item Active member of \textbf{NGO} Umeed working for upliftment of necessitous children .
\item Regular participant in contests held by various competive coding websites. Handle-\textbf{Siddharth2610}



\end{itemize} 

\end{document}
